Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-26 vesicle_code/docs/adhesion/adhesion.tex
new figures from yny

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.eps}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.eps}
\caption{\label{fig:qflow00} Scaling of the time it takes for two
  vesicles to reach equilibrium. {\em Left}: Scaling with respect to
  $\delta$ with $H=0.1$.  {\em Right}: Scaling with respect to $H$ with
  $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
  reached within $1\%$.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling01.png}
\includegraphics[keepaspectratio=true,scale=0.4]{figs/Dec13a_time_scaling02.png}
\caption{\label{fig:qflow00} Scaling of the time it takes for two
  vesicles to reach equilibrium. {\em Left}: Scaling with respect to
  $\delta$ with $H=0.1$.  {\em Right}: Scaling with respect to $H$ with
  $\delta = 0.4$. Arrows indicate the time by when the equilibrium is
  reached within $1\%$.}
\end{figure}
